\chapter{Dataset}\label{ch:dataset}

This chapter describes the preliminary work done on the dataset in order to
prepare it to train and test the intelligent systems described in the next
chapters.

The first stages of most pipelines used in this project are the following:
\begin{description}
\item[preparedata] This stage loads the data from the CSV files and builds a
	MATLAB structure with a field for each subject. Each field is a
	structure itself with a field for each activity containing a timetable
	with a column for each signal (including the ECG signal).
\item[fixdata] This stage checks that each timetable built in the previous
	stage do not contain any large ``hole'' (a long period of time without
	data). If such a hole is found, the timetable is splitted into 2
	timetables, creating a new subject. The resulting MATLAB structure has
	the same fields as before. In particular, this stage is used to fix the
	data of subject \texttt{s1} during the activity \texttt{sit} which has
	a large 1 hour hole in the middle of the data. A new subject
	(\texttt{s23}) is created with the only activity \texttt{sit}. From
	execution output:
	\begin{verbatim}
	*** STAGE fixdata ***
	Subject 1, activity sit: 2 DIFFERENT time deltas
	(largest: 01:03:06.917). Some are too large.
	Splitting...1-140932...140933-254026(->s23)...done!
	\end{verbatim}
\item[augmentdata] This stage performs data augmentation via random
	subsampling, as explained in \secref{sec:augmentdata}.
\item[getfeatures] This stage simply returns a list of features to extract. See
	\secref{subsec:getfeaturesstage}.
\item[extractfeatures] This stage extracts all the features specified by the
	previous stage (\texttt{getfeatures}) from the augmented dataset. This
	stage is described in details in \secref{subsec:extractfeaturesstage}.
\item[extracttargets] Extract the targets (ECG mean, standard deviation and
	activity) from the augmented dataset, as described in
	\secref{subsec:extracttargetsstage}.
\end{description}

\input{dataset/augmentdata}
\input{dataset/extractfeaturestargets}
\input{dataset/normalization}
