\chapter{ECG prediction using a Recurrent Neural Network}\label{ch:rnn}

In this chapter I will discuss the design and implementation of a Long
Short-Term Memory (LSTM) Recurrent Neural Network (RNN) that is able to predict
the next value of the ECG signal given as input the ECG signal up to the
previous time step and some other signals. This implements the requirements for
the Task 4.2 of the Project Specifications.

The approach followed to develop the RNN is similar to the one used in
\chref{ch:rnn}. In particular, since training of CNNs and RNNs is similar, the
script \code{rnntrain.m} is a copy-pasted and adapted version of the
\code{cnntrain.m} script.

Note that, for this task, I've changed again the way data augmentation is
performed. Here, I'll extract a total of \(60000\) samples of \(61\) time
steps, since \(6000\) samples were not sufficient to train the RNN. Moreover,
the \code{fixdata} stage is instructed to divide samples whenever a hole larger
than 2 milliseconds (the fastest sampling rate) is found in the data: to train
an RNN, I do not want to have any hole at all in the data.

The developed RNN uses 8 signals of the 11 signals available in the dataset.
The 8 signals selected are all the signals that are sampled with a sampling
rate of \(500\) Hz (the \code{pleth\_*} signals, the \code{temp\_3} signal
and, obiously, the \code{ecg} signal). This choice has been made in order to
avoid to use signals sampled at lower rates, which remain constants for some
time steps and may degrade the performance of the network.

\input{rnn/winsize}
\input{rnn/normalization}
\input{rnn/neurons}
\input{rnn/training}
\input{rnn/finalrnn}
